Appendix A

### 2020-09-21 appendixA/appendixA.Rmd
calc all parameters

```{r fig.height=6}
prms.fams.df %>% 
  dplyr::select(., loglik, n, dist, data) %>% 
  distinct() %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.BIC

popfam.BIC %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")

@@

Calculate BIC for the model at the family level
```{r}
prms.fams.df %>% 
  filter(., data != "pop") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "fam") %>% 
  full_join(., popfam.BIC %>% 
  filter(., data == "pop")) -> comp.fams

@@

# Get the multi-distribution model fit
popfam.BIC %>% 
  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
  ungroup() %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  as.numeric() -> multi.BIC

popfam.BIC %>% 
  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
  ungroup() %>% 
  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
  as.numeric() -> multi.AIC

popfam.BIC %>% 
  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
  ungroup() %>% 
  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
  as.numeric()-> multi.AICc

@@

>>>>

```{r fig.height=6}
prms.fams.df %>% 
  dplyr::select(., loglik, n, dist, data) %>% 
  distinct() %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.IC

popfam.IC %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")

@@

Calculate BIC for the model at the family level
```{r}
prms.fams.df %>% 
  filter(., data != "pop") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "fam") %>% 
  full_join(., popfam.IC %>% 
  filter(., data == "pop")) -> comp.fams

@@

# Get the multi-distribution model fit
popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
  ungroup() %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  as.numeric() -> multi.BIC

popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
  ungroup() %>% 
  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
  as.numeric() -> multi.AIC

popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
  ungroup() %>% 
  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
  as.numeric()-> multi.AICc

@@

```{r}
# Save parameters

saveRDS(popfam.IC, file = "data/popfamICprms.RDS")
saveRDS(popind.IC, file = "data/popindICprms.RDS")
